Quantum-assisted unsupervised data clustering

### 2020-05-08 manuscript.tex
resolving issue #49

In the general case when multiple input vectors are present in the register, the ``Decoding'' stage still needs to be included leading to larger circuit depth and less attractive complexity in terms of number of controlled gate operations.
The number of controlled gate operations in this general case of multiple input vectors is matching the number of controlled gate operations in \cite{trugenberger2001}.

>>>>

In the general case when multiple input vectors are present in the register, the ``Decoding'' stage still needs to be included leading to larger circuit depth and less attractive complexity in terms of number of controlled gate operations.
The number of controlled gate operations in this general case of multiple input vectors is matching the number of controlled gate operations in \cite{trugenberger2001} but the number of remaining gates is reduced compared to [80], leading to less deep circuit, which is significant for NISQ devices.
